% Propriété de Luis L. Marques et Enzo Carré
\documentclass[12pt, a4paper]{report}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[top = 2 cm, bottom = 2 cm, left = 2 cm, right = 2 cm]{geometry} % Page margins

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{algorithm,algorithmic}

\title{Object oriented programming}
\author{Luis L. marques\\Enzo Carré}
\date{2019/2020}

\begin{document}

\maketitle
\tableofcontents

\newpage
\section*{How to play}
\addcontentsline{toc}{section}{How to play}

The realm is in chaos after the king passed away. You are a duke and have to fight all the other aspiring dukes to get the throne. There are also neutral dukes who don't specially want the throne.

Your castle is the one with the red flag, while aspiring dukes's castles are the colored ones. The neutral dukes all have grey castles.

When clicking a castle, you have information displayed about it, even if it's an enemy castle. Then you will have many buttons in the top center of your screen.

The list in order is:

\begin{itemize}
    \item Recruit.
    \item Move (Move if ally target, Attack if enemy target).
    \item Level up castle.
    \item Transfer money between castles.
    \item Build wall around castle.
    \item Level up the castle's barrack.
\end{itemize}

With these commands, you should be able to play instinctively and have fun. The game is over once you have no more castles (lose) or when you conquered all the other active dukes (win).

\textbf{Note:} When transfering money, you can write the amount in the spinner. However, to transfer that amount, you first have to press Enter so the application gets the value you typed.

\section*{Making the game}
\addcontentsline{toc}{section}{The game}

\subsection*{Used tools}
\addcontentsline{toc}{subsection}{Used tools}

Because the course that ordered this project is based on the Java language, we had to use it along with JavaFX for the graphics.

As for the IDEs, we had a mix of Eclipse and IntelliJ users.

\subsection*{The basic version}
\addcontentsline{toc}{subsection}{The basic version}

The client ordered a basic and an advanced version of the game.

For the basic one, we had the following rules:

\begin{itemize}
    \item Only one type of troop. We chose to keep the knight.
    \item Only one level for castles.
    \item The troops don't evade castles or obstacles when moving.
    \item The troops don't leave the castle by the door.
    \item Per turn, castles produce troops instead of money.
    \item The bots don't do anything.
\end{itemize}

This was in order to have a first functional prototype without all the features, but that could be played by someone.

\subsection*{The advanced version}
\addcontentsline{toc}{subsection}{The advanced version}

For the advanced version, we took out the rules we specified in the previous subsection, and we added the following ones:

\begin{itemize}
    \item Many types of troops. We chose 3: Knight, Onager, Pikeman.
    \item Many levels for castles. We chose to have a max of 10.
    \item The troops evade castles and obstacles when moving.
    \item The troops leave the castle by the door.
    \item Per turn, castles produce money, and money can be used to create troops and level up the castle.
    \item The bots do actions.
\end{itemize}

\noindent{
As bonus features, not included in contract, we added:
}

\begin{itemize}
    \item Walls around the castles.
    \item A troop type that can move money from one castle to another.
    \item No victory screen.
\end{itemize}

\subsection*{Known bugs}
\addcontentsline{toc}{subsection}{Known bugs}

Basic version:

\begin{itemize}
    \item Randomly, the application won't start up.
    \item Sometimes, troops follow the path but are a bit off them when moving to another castle.
    \item After conquering a castle, sending troops again will make them appear twice, but the game only considers them once as we wanted.
    \item White bar on the right side of the window.
    \item Random crashes (problably AI related).
    \item No victory screen.
\end{itemize}

\noindent{
    Advanced version:
}

\begin{itemize}
    \item Randomly, the application won't start up.
    \item White bar on the right side of the window.
    \item Multiple recruitement has some bugs.
\end{itemize}

\section*{How we did the game}
\addcontentsline{toc}{section}{How we did the game}

We were two on the project. In the first part, we just started coding on the same parts to find what we could do using JavaFX.

\subsection*{The common work}
\addcontentsline{toc}{subsection}{The common work}

The common work was the design of the interfaces and classes we would use as well as the beginning of the code, as it was shared between both versions.

\subsection*{The personal work}
\addcontentsline{toc}{subsection}{The personal work}

By the time we had separated our project into the basic and the advanced version, we also deletaged work.

I took on the basic version along with the javadoc and the documentation for both versions while Enzo took on the advanced version.

\section*{Personal Experience}
\addcontentsline{toc}{section}{Personal Experience}

\subsection*{Luis L. Marques}
\addcontentsline{toc}{subsection}{Luis L. Marques}

Personnally, I found this project a bit boring at the beginning, as it is not my type of game, and I wasn't familiar with Java.

Afterwards, I familiarised myself with JavaFX. Althought it doesn't resemble any other library I already used, it was quite easy to use.

Contract side, I felt the contract had some unprecisions about the players and the attack system. I also felt we lacked a bit of time, one or two more weeks would have been perfect for our team.

Code side, it was a great opportunity to discover and master a new language, and as for every other project, it was a great opportunity to develop team-play.

\subsection*{Enzo Carré}
\addcontentsline{toc}{subsection}{Enzo Carré}



\end{document}